---
title: "p8105_hw6_ym3077"
output: github_document
---

```{r}
library(tidyverse)
library(broom)
library(modelr)
library(mgcv)
library(ggplot2)
library(p8105.datasets)
```

## Problem 1

Import the dataset.
```{r}
homicides_raw = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/refs/heads/master/homicide-data.csv")
```
    
    
Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.
```{r}
homicides_df = homicides_raw |>
  mutate(
    city_state = str_c(city, ", ", state),
    solved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age)
    ) |>
  filter(
    !(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
    victim_race %in% c("White", "Black")
  )
```
    
For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors.     
Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.
```{r}
baltimore_glm = homicides_df |>
  filter(city_state == "Baltimore, MD") |>
  glm(solved ~ victim_age + victim_race + victim_sex,
      data = _, 
      family = binomial())

baltimore_tidy = tidy(baltimore_glm, conf.int = TRUE) |>
  mutate(OR = exp(estimate),
         OR_low = exp(conf.low),
         OR_high = exp(conf.high))

baltimore_sexOR = baltimore_tidy |>
  filter(term == "victim_sexMale") |>
  select(term, OR, OR_low, OR_high) |>
  knitr::kable(digits = 3)
baltimore_sexOR
```
In Baltimore, after adjusting for victim age and race, the estimated odds of solved homicide are substantially lower for male victims compared with female victims. The adjusted odds ratio is 0.426 (95% CI: 0.324–0.558), indicating that homicides involving male victims have approximately 57% lower odds of being resolved. Because the confidence interval does not include 1, this association is statistically significant.
    
    
Now run `glm` for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. Do this within a “tidy” pipeline, making use of `purrr::map`, list columns, and `unnest` as necessary to create a dataframe with estimated ORs and CIs for each city.
```{r}
city_OR = homicides_df |>
  nest(data = -city_state) |>
  mutate(
    model = map(data, \(df)
                glm(solved ~ victim_age + victim_race + victim_sex, 
                    data = df, family = binomial())),
    tidy_result = map(model, \(mod) tidy(mod, conf.int = TRUE) |>
                        mutate(
                          OR = exp(estimate),
                          OR_low = exp(conf.low),
                          OR_high = exp(conf.high))
                        )) |>
  select(city_state, tidy_result) |>
  unnest(tidy_result) |>
  filter(term == "victim_sexMale") |>
  select(city_state, OR, OR_low, OR_high)

knitr::kable(city_OR, digits = 3)
```
    
    
    
Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}
city_OR_plot = city_OR |>
  mutate(
    city_state = fct_reorder(city_state, OR)) |>
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() +
  geom_errorbar(aes(ymin = OR_low, ymax = OR_high), width = 0.1) +
  coord_flip() +
  labs(
    x = "City", 
    y = "Adjusted OR (Male vs. Female victim)",
    title = "Adjusted ORs and 95% CIs for homicide being solved: male vs female victims"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 8), 
    plot.title = element_text(face = "bold", size = 11, hjust = 0.5)   
  )
city_OR_plot
```
The plot shows variation across cities in the adjusted odds ratio (OR) comparing the probability that male versus female homicide victims have their cases solved, after controlling for victim age and race. In general, Male homicide victims are less likely to have their cases solved than female victims (OR less than 1) in most cities, even after accounting for age and race. A few cities deviate from this pattern, but uncertainty is high in many of those cases.
      
      
        
## Problem 2

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities.
```{r}
data("weather_df")
set.seed(1)
```

```{r}
weather_boot <- 
  weather_df |> 
  drop_na(tmax, tmin, prcp) |>
  modelr::bootstrap(n = 5000) |>
  mutate(
    fit = map(strap, ~ lm(tmax ~ tmin + prcp, data = .x)),
    r2 = map_dbl(fit, ~ broom::glance(.x)$r.squared),
    beta_ratio = map_dbl(fit, ~ {
      coefs <- broom::tidy(.x)
      beta1 <- coefs |> filter(term == "tmin") |> pull(estimate)
      beta2 <- coefs |> filter(term == "prcp") |> pull(estimate)
      beta1 / beta2
    })
  ) |>
  select(-strap, -fit)
```
      
      
      
Plot the distribution of your estimates, and describe these in words.
```{r}
r2plot = weather_boot |>
  ggplot(aes(x = r2)) +
  geom_density() +
  labs(
    title = "Bootstrap Distribution of estimated R²",
    x = "estimated R²",
    y = "Density"
  ) +
  theme_minimal()
r2plot
```
The bootstrap distribution of R² is approximately symmetric, indicating across all repeated samples, the linear model `tmax ~ tmin + prcp` consistently explains the majority of the variability; `tmin` and `prcp` together provides a reliable prediction of `tmax`.
      
      
```{r}
ratioplot = weather_boot |>
  ggplot(aes(x = beta_ratio)) +
  geom_density() +
  labs(
    title = "Bootstrap Distribution of estimated β1 / β2",
    x = "estimated β1 / β2",
    y = "Density"
    ) +
  theme_minimal()
ratioplot
```
The bootstrap distribution of estimated β1 / β2 (ratio of the coefficient on tmin to the coefficient on prcp) is left-skewed, ranging from -400 to -100; suggesting large sampling variability in the ratio of coefficients. This is expected as ratios of cofficients are often unstable especially when one coefficient is near zero.

      
      
Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r² and β1 / β2 ratio
```{r}
weather_boot |>
  summarize(
    r2CI_low = quantile(r2, 0.025),
    r2CI_high = quantile(r2, 0.975),
    ratioCI_low = quantile(beta_ratio, 0.025),
    ratioCI_high = quantile(beta_ratio, 0.975)
  )
```
Using 5000 bootstrap samples, the 95% confidence interval for r² is approximately: (0.935, 0.947), the 95% confidence interval for the ratio of regression coefficients β1 and β2 is: (-278,\ -126).
    
    
   
## Problem 3
    
    
Load and clean the data for regression analysis (i.e. use appropriate variable names, convert numeric to factor where appropriate, check for the presence of missing data, etc.).
```{r}

```

```{r}

```


```{r}

```

```{r}

```










